Certified Symbolic Finite Transducers: Formalization and Applications to String Analysis

### 2025-09-04 Paper/application.tex
polish application

\section{Applications and Evaluation}
We evaluate our formalization and implementation of the SFT product operation across two key application domains: string sanitization and string replacement in string solving. These case studies highlight the practical value of our certified SFT product operation in real-world scenarios.
\subsection{Sanitizer}

>>>>

\section{Applications and Evaluation}
\label{sec:application}
We evaluate our formalization and implementation of the SFT product operation across two key application domains: string sanitization and string replacement in string solving. These case studies highlight the practical value of our certified SFT product operation in real-world scenarios.
\subsection{Sanitizer}

### 2025-09-04 Paper/introduction.tex
polish application

\paragraph{Organization.}
The remainder of this paper is organized as follows:
Section \ref{sec:motivation} provides several concrete motivating examples.
Section \ref{sec:formalization} introduces the formalization of symbolic finite transducers.
Section \ref{sec:product-operation} presents the product operation at the abstract level.
Section \ref{sec_alg_refinement} details the algorithmic refinement of the product operation.
Section \ref{sec-app-str-solver} demonstrates the application to string constraint solving.
Section \ref{sec:related-work} discusses related work.
Section \ref{sec:conclusion} concludes with future directions.

>>>>

\paragraph{Organization.}
The remainder of this paper is organized as follows:
Section \ref{sec:motivation} provides concrete motivating examples.
Section \ref{sec:sft} introduces the definition of symbolic finite transducers and their product operations.
Section \ref{sec:formalization} presents our formalization of SFTs in Isabelle/HOL.
Section \ref{sec:application} demonstrates applications to sanitizer analysis and string constraint solving.
Section \ref{sec:related-work} discusses related work.
Section \ref{sec:conclusion} concludes and outlines future directions.
